Manuscript 1 code

### 2024-10-25 manuscript_1_code.Rmd
removed evenness. Further streamlined themes and code.

## Figure formatting
```{r figure formatting info}
trends_theme <- theme_bw() + 
  theme(axis.title.x = element_text(size=24), 
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.y = element_text(size=24), 
        plot.title = element_text(size = 24),
        panel.background = element_rect(fill = "white"), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_rect(fill = "white"),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_blank(),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))

@@

# ggsave(filename = "output/figure_1v3.png", figure_1, height = 10, width = 14)
```

@@

#JG Add Evenness
alpha_diversity_quad_macro$ev <- alpha_diversity_quad_macro$shannon /
  (log(alpha_diversity_quad_macro$richness))

#makes 1 species 0 and 0 species NA for evenness metric
alpha_diversity_quad_macro$evenness <- ifelse(
  alpha_diversity_quad_macro$richness == 0,
  NA,
  # If richness == 0, ev is NA
  ifelse(
    alpha_diversity_quad_macro$richness == 1,
    0,
    # If richness == 1, ev is 0
    alpha_diversity_quad_macro$ev
  )
)

alpha_diversity_quad_macro <- merge(meta_df, alpha_diversity_quad_macro, by = c("location", "year"))
alpha_diversity_quad_macro$evenness[is.na(alpha_diversity_quad_macro$evenness)] <- 0
```

@@

```{r site level evenness}
#JG Add Evenness
alpha_diversity_site_macro$ev <- alpha_diversity_site_macro$shannon /
  (log(alpha_diversity_site_macro$richness))

#makes 1 species 0 and 0 species NA for evenness metric
alpha_diversity_site_macro$evenness <- ifelse(
  alpha_diversity_site_macro$richness == 0,
  NA,
  # If richness == 0, ev is NA
  ifelse(
    alpha_diversity_site_macro$richness == 1,
    0,
    # If richness == 1, ev is 0
    alpha_diversity_site_macro$ev
  )
)

alpha_diversity_site_macro <- left_join(site_meta_df, alpha_diversity_site_macro,by = join_by(year, site, habitat, site_habitat))
# prior transformation did not properly set 0 values for evenness
alpha_diversity_site_macro$evenness[is.na(alpha_diversity_site_macro$evenness)] <- 0
```

@@

### plot
```{r figure 2a}
(figure_2a <- ggplot() +
  geom_point(data = quad_richness_df, aes(x = year, y = richness_mean, colour = habitat), size = 4,
             position = position_dodge(0.4)) +
  geom_line(data = quad_richness_df, aes(x = year, y = richness_mean, colour = habitat), linewidth = 1) +
  geom_errorbar(data = quad_richness_df, aes(x = year, ymin = richness_mean - richness_se, ymax = richness_mean + richness_se,
                                             colour = habitat), width = 0, size = 1.3, position = position_dodge(0.4)) +
  scale_colour_manual(values = habitat_colours) +
  # scale_fill_manual(values = habitat_colours) +
  #geom_segment(aes(y = 75, yend = 75, x = 2006, xend = 2010), linewidth = 2, colour = "grey") +
  annotate("segment", x = 2006, xend = 2010, y = 2, yend = 2, linewidth = 2, colour = "grey") +
  geom_vline(xintercept = 2010, linetype = 2, colour = "black", size = 1) +
  geom_vline(xintercept = 2019, linetype = 2, colour = "red", size = 1) +
   scale_x_continuous(breaks = unique(quad_richness_df$year)) +
   labs(y = "Macroalgal Richness",
        x = "Year",
        title = "Quadrat-level Richness") +
   trends_theme)

@@

### plot
```{r plot figure 2b}
(figure_2b <- ggplot() +
  geom_point(data = site_richness_df, aes(x = year, y = richness_mean, colour = habitat), size = 4,
             position = position_dodge(0.4)) +
#  geom_jitter(data = alpha_diversity_site_macro, 
#  aes(x = year, y = richness, colour = habitat, alpha = 0.05), size = 2, width = 0.4, height = 0) +
  geom_line(data = site_richness_df, aes(x = year, y = richness_mean, colour = habitat), linewidth = 1) +
  geom_errorbar(data = site_richness_df, aes(x = year, ymin = richness_mean - richness_se, ymax = richness_mean + richness_se, colour = habitat), size = 1.3, width = 0,  position = position_dodge(0.4)) +
  scale_colour_manual(values = habitat_colours) +
  #geom_segment(aes(y = 75, yend = 75, x = 2006, xend = 2010), linewidth = 2, colour = "grey") +
  annotate("segment", x = 2006, xend = 2010, y = 12, yend = 12, linewidth = 2, colour = "grey") +
  geom_vline(xintercept = 2010, linetype = 2, colour = "black", size = 1) +
  geom_vline(xintercept = 2019, linetype = 2, colour = "red", size = 1) +
   scale_x_continuous(breaks = unique(site_richness_df$year)) +
   labs(y = "",
        x = "Year",
        title = "Site-level Richness") +
  trends_theme)

@@

## Figure 2 Full Plot
```{r ggpubr fig2, fig.height = 10, fig.width=22}
fig2_plot_list <- list(figure_2a, figure_2b)
(figure_2 <- ggarrange(plotlist = fig2_plot_list, 
                      ncol = 2, nrow = 1, 
                      labels = c("a.", "b."),
                      common.legend = TRUE,
                      legend = "bottom", 
                      font.label = list(size = 24, color = "black", face = "plain")))

# ggsave(filename = "output/figure_2v3.png", figure_2, height = 10, width = 22)
```

@@

## figure 3a plot setup
```{r figure 3a setup}
diversity_ranges_quad <- alpha_diversity_quad_macro %>%
  group_by(habitat) %>%
  summarise(min_richness = min(richness),
            max_richness = max(richness),
            min_cover= min(cover_trans),
            max_cover = max(cover_trans))

@@

filtered_cover_effects <- cover_emm %>%
  left_join(diversity_ranges_quad, by = c("habitat")) %>%
  filter(richness >= min_richness & richness <= max_richness)

@@

fg_summary_site_wide <- fg_summary_site_wide_SUM 
```

### model
```{r functional richness cover mod quad}
#merge Noam's data with functional group summary 
functional_richness_quad_cover <- merge(alpha_diversity_quad_macro, fg_summary_wide,
                                        by = c("location", "year", "site", "habitat"))

@@

```{r site level fg richness model}
#merge site level cover with site functional group richness

functional_richness_site_cover<- merge(alpha_diversity_site_macro, fg_summary_site_wide,
                                by = c("year", "site",  "habitat"))

@@

## evenness over time
```{r evenness over time quad,  fig.height = 10, fig.width = 14}

quad_evenness_df <- alpha_diversity_quad_macro %>% 
  drop_na(evenness) %>%
  group_by(year, habitat) %>% 
  summarise(evenness_mean = mean(evenness),
            evenness_se = se(evenness))

(evenness_time_quad <- ggplot() +
  geom_point(data = quad_evenness_df, aes(x = year, y = evenness_mean, colour = habitat), size = 3) +
  geom_line(data = quad_evenness_df, aes(x = year, y = evenness_mean, colour = habitat), linewidth = 1) +
  geom_errorbar(data = quad_evenness_df, aes(x = year, ymin = evenness_mean - evenness_se, ymax = evenness_mean + evenness_se,
                                             colour = habitat), width = 0, size = 1.3) +
  scale_colour_manual(values = habitat_colours) +
  # scale_fill_manual(values = habitat_colours) +
  #geom_segment(aes(y = 75, yend = 75, x = 2006, xend = 2010), linewidth = 2, colour = "grey") +
  annotate("segment", x = 2006, xend = 2010, y = .7, yend = .7, linewidth = 2, colour = "grey") +
  geom_vline(xintercept = 2010, linetype = 2, colour = "black", size = 1) +
  geom_vline(xintercept = 2019, linetype = 2, colour = "red", size = 1) +
   scale_x_continuous(breaks = unique(quad_evenness_df$year)) +
   labs(y = "Macroalgal evenness \n",
        x = "Year",
        title = "c. Quadrat-level evenness") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=24), 
        axis.text.x = element_text(angle = 45, hjust = 1, size = 22),
        axis.text.y = element_text( size = 22),
        axis.title.y = element_text(size=24), 
        plot.title = element_text(size=26),
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_rect(fill = "white"),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_blank(),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black")) )

# ggsave(filename = "output/evenness_time_quad.png", evenness_time_quad, height = 10, width = 14)
```

##  Evenness @ Site by Year
```{r evenness over time quad,  fig.height = 10, fig.width = 14}
site_evenness_df <- alpha_diversity_site_macro %>% 
  drop_na(evenness) %>%
  group_by(year, habitat) %>% 
  summarise(evenness_mean = mean(evenness),
            evenness_se = se(evenness))

(evenness_time_site <- ggplot() +
  geom_point(data = site_evenness_df, aes(x = year, y = evenness_mean, colour = habitat), size = 3) +
  geom_line(data = site_evenness_df, aes(x = year, y = evenness_mean, colour = habitat), linewidth = 1) +
  geom_errorbar(data = site_evenness_df, aes(x = year, ymin = evenness_mean - evenness_se, ymax = evenness_mean + evenness_se, colour = habitat), size = 1.3, width = 0) +
  scale_colour_manual(values = habitat_colours) +
  #geom_segment(aes(y = 75, yend = 75, x = 2006, xend = 2010), linewidth = 2, colour = "grey") +
  annotate("segment", x = 2006, xend = 2010, y = 1, yend = 1, linewidth = 2, colour = "grey") +
  geom_vline(xintercept = 2010, linetype = 2, colour = "black", size = 1) +
  geom_vline(xintercept = 2019, linetype = 2, colour = "red", size = 1) +
   scale_x_continuous(breaks = unique(site_evenness_df$year)) +
   labs(y = "Macroalgal evenness \n",
        x = "Year",
        title = "Site-level evenness") +
  theme_bw() + 
  theme_bw() + 
  theme(axis.title.x = element_text(size=24), 
        axis.text.x = element_text(angle = 45, hjust = 1, size = 22),
        axis.text.y = element_text( size = 22),
        axis.title.y = element_text(size=24), 
        plot.title = element_text(size=26),
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_rect(fill = "white"),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_blank(),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black")) )

# ggsave(filename = "output/evenness_time_site.png", evenness_time_site, height = 10, width = 14)
```

## evenness and cover relationships

```{r evenness cover quad level model}

# NOTE: I tried transforming evenness and the trends/plot were basically identical, just on a different scale. There's no fixing a shit sandwich - Noam
evenness_cover_mod_quad <- glmmTMB(cover_trans ~ evenness*habitat + (1|site/location) + (1|year), family = beta_family(), data = alpha_diversity_quad_macro)
summary(evenness_cover_mod_quad)
Anova(evenness_cover_mod_quad)
#                    Chisq Df Pr(>Chisq)    
# evenness         9226.79  1  < 2.2e-16 ***
# habitat           270.78  3  < 2.2e-16 ***
# evenness:habitat  411.03  3  < 2.2e-16 ***
hist(residuals(evenness_cover_mod_quad)) # slight pos skeq
plot(residuals(evenness_cover_mod_quad) ~ fitted(evenness_cover_mod_quad))
r.squaredGLMM(evenness_cover_mod_quad) # 0.38, 0.46
emtrends(evenness_cover_mod_quad, pairwise ~ habitat, var = "evenness") # everything different
#  contrast                    estimate     SE  df z.ratio p.value
#  Fringing - Backreef           -0.206 0.0708 Inf  -2.904  0.0193
#  Fringing - Forereef 10m        0.491 0.0679 Inf   7.228  <.0001
#  Fringing - Forereef 17m        0.920 0.0689 Inf  13.361  <.0001
#  Backreef - Forereef 10m        0.696 0.0581 Inf  11.994  <.0001
#  Backreef - Forereef 17m        1.126 0.0595 Inf  18.925  <.0001
#  Forereef 10m - Forereef 17m    0.429 0.0551 Inf   7.794  <.0001

```{r evenness cover plot setup}
diversity_ranges_quad_evenness <- alpha_diversity_quad_macro %>%
  group_by(habitat) %>%
  summarise(min_evenness = min(evenness),
            max_evenness = max(evenness),
            min_cover= min(cover_trans),
            max_cover = max(cover_trans))

cover_emm_evenness <- emmip(evenness_cover_mod_quad,
                        habitat ~ evenness,
                        at = list(evenness = seq(0,10,1)), plotit = F, CIs = T)

filtered_cover_effects_evenness <- cover_emm_evenness %>%
  left_join(diversity_ranges_quad_evenness, by = c("habitat")) %>%
  filter(evenness >= min_evenness & evenness <= max_evenness)

```{r evenness cover plot}
(evenness_cover_quad_plot <- 
  ggplot() +
  geom_point(data = alpha_diversity_quad_macro,
             aes(x = evenness, y = cover_trans, colour = habitat), size = 1, alpha = 1) + 
  geom_line(data = filtered_cover_effects_evenness, aes(x = evenness, y = inv_logit(yvar), colour = habitat)) +
  geom_ribbon(data = filtered_cover_effects_evenness, aes(x = evenness, ymin = inv_logit(LCL), ymax = inv_logit(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "Cover\n", x = "Macroalgal evenness", title = "") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_rect(fill = "white"),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_blank(),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

# ggsave(filename = "output/evenness_cover_quad.png", evenness_cover_quad_plot, height = 10, width = 14)
```

## site level evenness versus cover

```{r site level evenness}

evenness_site_cover_mod <- glmmTMB(cover_trans ~ evenness*habitat + (1|site_habitat) + (1|year), family = beta_family(), data = alpha_diversity_site_macro)
summary(evenness_site_cover_mod)
Anova(evenness_site_cover_mod)
#                    Chisq Df Pr(>Chisq)   
# evenness          8.1578  1   0.004288 **
# habitat           6.6305  3   0.084654 . 
# evenness:habitat 14.6557  3   0.002136 ** 
hist(residuals(evenness_site_cover_mod)) # some positive skew, not the worst thing ever
plot(residuals(evenness_site_cover_mod) ~ fitted(evenness_site_cover_mod)) # a little heteroscedastic but can't be less than 0
r.squaredGLMM(evenness_site_cover_mod) # 0.1300791 0.5988565
emtrends(evenness_site_cover_mod, pairwise ~ habitat, var = "evenness") # only the outers are different from each other
# contrast                    estimate    SE  df z.ratio p.value
# Fringing - Backreef            0.967 0.545 Inf   1.774  0.2860
# Fringing - Forereef 10m        1.258 0.409 Inf   3.073  0.0114
# Fringing - Forereef 17m       -0.228 0.459 Inf  -0.497  0.9597
# Backreef - Forereef 10m        0.292 0.563 Inf   0.517  0.9549
# Backreef - Forereef 17m       -1.195 0.595 Inf  -2.007  0.1854
# Forereef 10m - Forereef 17m   -1.486 0.472 Inf  -3.146  0.0090
```
### plot

```{r  evenness site plot }
diversity_ranges_site_evenness <- alpha_diversity_site_macro %>%
  group_by(habitat) %>%
  summarise(min_evenness = min(evenness),
            max_evenness = max(evenness),
            min_cover= min(cover_trans),
            max_cover = max(cover_trans))

cover_emm_evenness_site <- emmip(evenness_site_cover_mod,
                        habitat ~ evenness,
                        at = list(evenness = seq(0,1,0.01)), plotit = F, CIs = T)

filtered_cover_effects_evenness_site <- cover_emm_evenness_site %>%
  left_join(diversity_ranges_site_evenness, by = c("habitat")) %>%
  filter(evenness >= min_evenness & evenness <= max_evenness)

(evenness_cover_site_plot <- 
  ggplot() +
  geom_point(data = alpha_diversity_site_macro,
             aes(x = evenness, y = cover_trans, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_cover_effects_evenness_site, aes(x = evenness, y = inv_logit(yvar), colour = habitat)) +
  geom_ribbon(data = filtered_cover_effects_evenness_site, aes(x = evenness, ymin = inv_logit(LCL), ymax = inv_logit(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "Cover\n", x = "Macroalgal evenness", title = "3f. Site Level Evenness") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_rect(fill = "white"),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_blank(),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

# ggsave(filename = "output/evenness_cover_site.png", evenness_cover_site_plot, height = 10, width = 14)
```

## evenness stability

### quad level mod

```{r evenness stability quad mod}
even_stab_mod_quad <- glmmTMB(cover_stability~ evenness_mean*habitat + (1|site), family = Gamma("log"), data = diversity_stability_synchrony)
summary(even_stab_mod_quad)
Anova(even_stab_mod_quad)

#                          Chisq Df Pr(>Chisq)    
# evenness_mean         1235.417  1    < 2e-16 ***
# habitat                292.670  3    < 2e-16 ***
# evenness_mean:habitat   13.518  3    0.00364 ** 
hist(residuals(even_stab_mod_quad)) # slight positive skew
plot(residuals(even_stab_mod_quad) ~ fitted(even_stab_mod_quad)) 
r.squaredGLMM(even_stab_mod_quad) # 0.6582154 0.6582154
emtrends(even_stab_mod_quad, pairwise ~ habitat, var = "evenness_mean") # forereef 10 diff from fringe and backreef
# contrast                    estimate    SE  df z.ratio p.value
# Fringing - Backreef          -0.0123 0.151 Inf  -0.082  0.9998
# Fringing - Forereef 10m       0.4039 0.148 Inf   2.725  0.0326
# Fringing - Forereef 17m       0.3023 0.140 Inf   2.152  0.1368
# Backreef - Forereef 10m       0.4162 0.140 Inf   2.979  0.0153
# Backreef - Forereef 17m       0.3146 0.131 Inf   2.394  0.0782
# Forereef 10m - Forereef 17m  -0.1016 0.129 Inf  -0.790  0.8589

even_stab_emm <- emmip(even_stab_mod_quad,
                        habitat ~ evenness_mean,
                        at = list(evenness_mean = seq(0,1,0.01)), plotit = F, CIs = T)

filtered_even_stab_effects <- even_stab_emm %>%
  left_join(dss_ranges, by = c("habitat")) %>%
  filter(evenness_mean >= min_evenness & evenness_mean <= max_evenness)

(even_stab_plot <- 
  ggplot() +
  geom_point(data = diversity_stability_synchrony,
             aes(x = evenness_mean, y = cover_stability, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_even_stab_effects, aes(x = evenness_mean, y = exp(yvar), colour = habitat), size = 1.5) +
  geom_ribbon(data = filtered_even_stab_effects, aes(x = evenness_mean, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "Stability\n", x = "Evenness", title = "") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=24), 
        axis.title.y = element_text(size=24), 
        axis.text.x = element_text(size=22), 
        axis.text.y = element_text(size=22),
        legend.text = element_text(size=22),
        plot.title = element_text(size=26), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_rect(fill = "white"),
        legend.title = element_blank(),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

# ggsave(filename = "output/evenness_stability_quad.png", even_stab_plot, height = 10, width = 14)
```

## site level evenness stability

```{r site level evenness}
even_stab_mod_site <- glmmTMB(cover_stability~ evenness_mean*habitat, family = Gamma("log"), data = diversity_stability_synchrony_site)
summary(even_stab_mod_site)
Anova(even_stab_mod_site)

#                         Chisq Df Pr(>Chisq)   
# evenness_mean          0.1035  1   0.747623   
# habitat               11.8743  3   0.007827 **
# evenness_mean:habitat  9.6254  3   0.022034 * 
hist(residuals(even_stab_mod_site)) # a little chunky
plot(residuals(even_stab_mod_site) ~ fitted(even_stab_mod_site)) 
r.squaredGLMM(even_stab_mod_site) # 0.51
emtrends(even_stab_mod_site, pairwise ~ habitat, var = "evenness_mean") # no diff
# contrast                    estimate   SE  df z.ratio p.value
# Fringing - Backreef             2.82 1.66 Inf   1.705  0.3210
# Fringing - Forereef 10m         8.30 3.70 Inf   2.244  0.1115
# Fringing - Forereef 17m         4.27 1.94 Inf   2.205  0.1219
# Backreef - Forereef 10m         5.48 3.82 Inf   1.432  0.4793
# Backreef - Forereef 17m         1.45 2.17 Inf   0.668  0.9093
# Forereef 10m - Forereef 17m    -4.03 3.95 Inf  -1.019  0.7385

even_stab_emm_site <- emmip(even_stab_mod_site,
                        habitat ~ evenness_mean,
                        at = list(evenness_mean = seq(0,1,0.01)), plotit = F, CIs = T)

filtered_even_stab_effects_site <- even_stab_emm_site %>%
  left_join(dss_ranges, by = c("habitat")) %>%
  filter(evenness_mean >= min_evenness & evenness_mean <= max_evenness)
# This is useless
(even_stab_plot_site <- 
  ggplot() +
  geom_point(data = diversity_stability_synchrony_site,
             aes(x = evenness_mean, y = cover_stability, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_even_stab_effects_site, aes(x = evenness_mean, y = exp(yvar), colour = habitat), size = 1.5) +
  geom_ribbon(data = filtered_even_stab_effects_site, aes(x = evenness_mean, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "Stability\n", x = "Evenness", title = "") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=24), 
        axis.title.y = element_text(size=24), 
        axis.text.x = element_text(size=22), 
        axis.text.y = element_text(size=22),
        legend.text = element_text(size=22),
        plot.title = element_text(size=26), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_rect(fill = "white"),
        legend.title = element_blank(),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )
# ggsave(filename = "output/evenness_stability_site.png", even_stab_plot_site, height = 10, width = 14)
```

>>>>

## Figure formatting
```{r figure formatting info}
trends_theme <- theme_bw() + 
  theme(axis.title.x = element_text(size=24), 
        axis.text.x = element_text(size = 22, angle = 45, hjust = 1),
        axis.title.y = element_text(size=24), 
        axis.text.y = element_text(size = 22),
        plot.title = element_text(size = 24),
        panel.background = element_rect(fill = "white"), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_rect(fill = "white"),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_blank(),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))

@@

# ggsave(filename = "output/figure_1v4.png", figure_1, height = 10, width = 14)
```

@@

alpha_diversity_quad_macro <- merge(meta_df, alpha_diversity_quad_macro, by = c("location", "year"))

@@

@@

### plot
```{r figure 2a}
(figure_2a <- ggplot() +
  geom_point(data = quad_richness_df, aes(x = year, y = richness_mean, colour = habitat), size = 4,
             position = position_dodge(0.4)) +
  geom_line(data = quad_richness_df, aes(x = year, y = richness_mean, colour = habitat), linewidth = 1) +
  geom_errorbar(data = quad_richness_df, aes(x = year, ymin = richness_mean - richness_se, ymax = richness_mean + richness_se,
                                             colour = habitat), width = 0, size = 1.3, position = position_dodge(0.4)) +
  scale_colour_manual(values = habitat_colours) +
  annotate("segment", x = 2006, xend = 2010, y = 2, yend = 2, linewidth = 2, colour = "grey") +
  geom_vline(xintercept = 2010, linetype = 2, colour = "black", size = 1) +
  geom_vline(xintercept = 2019, linetype = 2, colour = "red", size = 1) +
   scale_x_continuous(breaks = unique(quad_richness_df$year)) +
   labs(y = "Macroalgal Richness",
        x = "Year",
        title = "") +
   trends_theme)

@@

### plot
```{r plot figure 2b}
(figure_2b <- ggplot() +
  geom_point(data = site_richness_df, aes(x = year, y = richness_mean, colour = habitat), size = 4,
             position = position_dodge(0.4)) +
#  geom_jitter(data = alpha_diversity_site_macro, 
#  aes(x = year, y = richness, colour = habitat, alpha = 0.05), size = 2, width = 0.4, height = 0) +
  geom_line(data = site_richness_df, aes(x = year, y = richness_mean, colour = habitat), linewidth = 1) +
  geom_errorbar(data = site_richness_df, aes(x = year, ymin = richness_mean - richness_se, ymax = richness_mean + richness_se, colour = habitat), size = 1.3, width = 0,  position = position_dodge(0.4)) +
  scale_colour_manual(values = habitat_colours) +
  annotate("segment", x = 2006, xend = 2010, y = 12, yend = 12, linewidth = 2, colour = "grey") +
  geom_vline(xintercept = 2010, linetype = 2, colour = "black", size = 1) +
  geom_vline(xintercept = 2019, linetype = 2, colour = "red", size = 1) +
   scale_x_continuous(breaks = unique(site_richness_df$year)) +
   labs(y = "",
        x = "Year",
        title = "") +
  trends_theme)

@@

## Figure 2 Full Plot
```{r ggpubr fig2, fig.height = 10, fig.width=22}
fig2_plot_list <- list(figure_2a, figure_2b)
(figure_2 <- ggarrange(figure_2a, figure_2b,
                      ncol = 2, nrow = 1, 
                      labels = c("a.", "b."),
                      common.legend = TRUE,
                      legend = "bottom", 
                      font.label = list(size = 24, color = "black", face = "plain")))

# ggsave(filename = "output/figure_2v4.png", figure_2, height = 10, width = 22)
```

@@

## figure 3a plot setup
```{r figure 3a setup}

diversity_ranges_quad <- extract_ranges(alpha_diversity_quad_macro, "habitat", c("richness", "cover_trans"))

@@

filtered_cover_effects <- filter_ranges(trend = cover_emm, range_obj = diversity_ranges_quad, group = "habitat", value = "richness")

@@

fg_summary_site_wide <- fg_summary_site_wide_SUM

#merge Noam's data with functional group summary 
functional_richness_quad_cover <- merge(alpha_diversity_quad_macro, fg_summary_wide,
                                        by = c("location", "year", "site", "habitat"))

#merge site level cover with site functional group richness
functional_richness_site_cover<- merge(alpha_diversity_site_macro, fg_summary_site_wide,
                                by = c("year", "site",  "habitat"))
```

### model
```{r functional richness cover mod quad}

@@

```{r site level fg richness model}

@@
